A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-07-08 faculty.tex
updates

\chapter{Research}
\chapter{Obtaining Funding}
Getting funding is arguably the most important part of getting tenure.  Writing grant propsal is very different from writing research papers. However, without funding, you can't pay your students, conference registration and travel, or even your own summer salary. %In short, the lack of funding causes lost of stress, uncertainty, and threaten your career.
Most new professors struggle with grant writing at first, but eventually get better at it.  In this chapter, we will discuss the various ways to obtain funding.

@@

\chapter{Teaching}
\section{Teaching Load}
\section{Teaching Evaluation}
\section{Teaching Philosophy}
\section{Teaching Awards}

@@

\subsection{Tenure Visits and Colloqium} Close to the tenure application (e.g., during the Spring), some tenure candidates will visit other universities to give talks and meet people. 
Sometimes the candidate is assigned to be the chair of the colloquium in the department, and they can invite their potential tenure letter writers to give talks.
These are all good ways to get your name out and to get letters.
The traditional way is a physical visit, but since the pandemic, many of these visits are done remotely (which are more convenient for many people).

I did not do any tenure visits or host anyone for the purpose of getting tenure letters. This was partly because I am not a travel person, and also I felt that it would not help much in my case; I believe that I have strong record and very good relationship with my colleagues and the dept.  Instead, during the Spring'23 semester before my tenure application, I put lots of effort in helping the university in recruiting faculty (by meeting with 20+ faculty candidates), even though I am not in the search committee and really didn't have service requirements as I am on study break that semester.  As mentioned in \autoref{sec:services-dept}, I didn't really do any of these for my tenure case, but because I enjoy the working env at GMU and want to help out.

>>>>

\chapter{Research}
\chapter{Obtaining Funding}
Getting funding is arguably the most important part of getting tenure.  without funding, you can't pay your students, conference registration and travel, or even your own summer salary. However, writing grant proposals is very different from writing research papers. Thus, most new professors struggle with grant writing at first, but eventually get better at it.

@@

\chapter{Teaching}
\section{Teaching Load}
\section{Teaching Evaluation}

At the end of each semester, students are asked to evaluate the instructor. The results are shared anonymously with the instructor to help them improve their teaching and course. Teaching evaluation is also commonly used in annual and tenure evaluation.

One main issue with teaching evaluation is that not many students respond, despite multiple reminders and urging from the instructor.  Moreover, the few that respond are usually the students who are unhappy and thus will give highly negative evaluation. This is the reason why many instructors do not like teaching evaluations, especially when it is used to evaluate their performance.

A strategy that I found effective is giving the entire class a small bonus point if everyone completes the evaluation. The bonus is computed as the percentage of responses * the bonus (X). So if X is 0.5 and everyone responds, everyone gets 0.5 points. If 50\% respond, each gets 0.25 points. While X is a tiny number, I emphasize that it can make a difference for borderline grades.  I don’t curve grades, so this is the only way for students to bump. I also emphasize that in my previous classes many students benefit from this.  So that really triggers their interest.  And also because evaluations are before final exams, everyone is incentivized to participate because they don’t know their final grades and don’t want to miss this opportunity.  Not only the students do it, they also remind their classmates/friends to do it.

I only employ this method recently, and response rate has been very good so far.  For Spr’24, it was 90\% (25/28 students) and for F’23, it was 100\% (16/16 students).  Before this, my response rate is about 50\%.

\section{Teaching Philosophy}
\section{Teaching Awards}

@@

\subsection{Tenure Visits and Colloquium} Closer to the tenure application (e.g., during the Spring), some candidates will visit other universities to give talks and meet people. 
Sometimes the candidate is assigned to be the chair of the colloquium in the department, and they can invite their potential tenure letter writers to give talks.
Both are good ways to get your name out and to get letters.
The traditional way is a physical visit, but since the pandemic, many of these visits are done remotely, which is more convenient for many people.

I did not do these visits, partly because I am not a travel person, and also I felt that I would not have problems finding letter writers.
Instead, during the Spring'23 semester before my tenure application, I put lots of effort in helping the university in recruiting faculty (by meeting with 20+ faculty candidates), even though I am not in the search committee and really didn't have service requirements during this pre-tenure study break. This helps me build a good relationship with my colleagues in the dept.
